\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=0.75in,right=0.75in,top=0.6in,bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
% Formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}
\begin{document}
\pagestyle{empty}
% Header
\begin{center}
    {\Huge \textbf{CHINMAY HARISH}} \\ \vspace{2pt}
    {\Large Associate Product Manager} \\ \vspace{4pt}
    Bengaluru, Karnataka $\cdot$ chinmayharish03@gmail.com $\cdot$ +91 9449124052 \\ \vspace{5pt}
    \href{https://github.com/ChinmayHarish}{\Large\faGithub} \quad
    \href{https://www.linkedin.com/in/chinmay-harish-03106t/}{\Large\faLinkedin} \quad
    \href{https://chinmay-portfolio-p1.netlify.app/}{\Large\faGlobe}
\end{center}
% Summary
\section{Summary}
Data driven Associate Product Manager with a strong foundation in analytics and a passion for building user centric products. Eager to leverage experience in launching Zero to One products and optimizing growth funnels to solve complex problems in a dynamic environment. Committed to driving product innovation and delivering measurable business impact.
% Experience
\section{Experience}
\noindent \textbf{Primenumbers Technologies Pvt Ltd.} \hfill Bengaluru, India \\
\textit{Associate Product Manager} \hfill July 2023 -- Present
\begin{itemize}[noitemsep,topsep=3pt,leftmargin=*]
    \item \textbf{Zero to One Product Launch (Infiniteworks):} Led end to end lifecycle of a new BI tool. Validated market gap via user interviews and successfully launched the product, aggregating \textbf{80,000+ opportunities}.
    \item \textbf{Strategic Leadership:} Defined roadmap, pricing, and Go To Market strategy. Built operations team by hiring \textbf{3 roles} (QA, Research, Lead Qual) and established Agile workflows (Jira) for on time delivery.
    \item \textbf{Feature Innovation:} Spearheaded the development of a proprietary 'Competitive Intelligence' module, enabling businesses to analyze competitor financials, significantly enhancing the platform's unique value proposition.
    \item \textbf{Product Execution:} Authored detailed Product Requirement Documents (PRDs) and user stories, prioritizing features based on engineering feasibility and user impact to ensure rapid MVP delivery.
    \item \textbf{Revenue Growth (Palladium):} Devised "Missed Bids" email campaign to reactivate leads, contributing to a \textbf{₹2 Cr annual revenue} pipeline. Revamped signup strategy, reducing attrition by \textbf{60\%}.
    \item \textbf{Funnel Optimization (Bidfortune):} Identified revenue avenues via competitive teardowns. Redesigned signup flow (8 to 5 steps) and integrated social login, reducing drop offs by \textbf{30\%}.
    \item \textbf{Analytics \& SEO (Rera Explorer):} Developed SQL dashboards to monitor data pipeline health (99% accuracy). Executed SEO strategy driving organic traffic growth.
\end{itemize}
\vspace{6pt}
\noindent \textbf{Primenumbers Technologies Pvt Ltd.} \hfill Bengaluru, India \\
\textit{Data Analyst Intern} \hfill March 2023 -- June 2023
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
    \item Designed and automated complex SQL reporting dashboards to provide real time data visibility for business decisions.
    \item Conducted A/B testing and user behavior analysis. Optimized SQL queries, reducing retrieval latency by \textbf{15\%}.
\end{itemize}
\vspace{6pt}
\noindent \textbf{BASF India} \hfill Mangalore, India \\
\textit{Student Intern} \hfill 2 Months
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
    \item Collaborated with senior scientists in a top 3 global Refinish Lab, working with clients like \textbf{Tata Motors} and \textbf{Mahindra}.
    \item Formulated and color matched \textbf{2 refinish coating colors} for the \textbf{Tata Nexon EV}, meeting strict quality standards.
\end{itemize}
% Education
\section{Education}
\noindent \textbf{B.M.S College of Engineering} \hfill Bengaluru, Karnataka \\
\textit{B.E. in Chemical Engineering} (CGPA: 8.8/10) \hfill Graduated: 2023
% Skills
\section{Technical Skills}
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
    \item \textbf{Data \& Analytics:} PostgreSQL, Mixpanel, Google Analytics, Postman.
    \item \textbf{Product Management:} Jira, Trello, Linear, Notion.
    \textbf{Design \& Prototyping:} Figma, Whimsical, Canva.
    \item \textbf{Methodologies:} Scrum, A/B Testing, User Research, GTM Strategy, Roadmap Planning, PRD Writing, Competitive Analysis.
\end{itemize}
% Certifications
\section{Certifications}
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
    \item \textbf{Product Management:} Mastering Product-Led Growth (2024)
    \item \textbf{AI \& Engineering:} ChatGPT Engineering for Developers
    \item \textbf{Data:} Intermediate SQL for Marketers and Product Managers (Codecademy)
\end{itemize}
\end{document}
